```{r echo=FALSE}
yml_content <- yaml::read_yaml("chapterauthors.yml")
author <- yml_content[["hydrology-analysis"]][["author"]]
```
# Lab Title {#hydrology-analysis}

Written by
```{r results='asis', echo=FALSE}
cat(author)
```

## Lab Overview {.unnumbered}

Lorem ipsum

------------------------------------------------------------------------

## Learning Objectives {.unnumbered}

-   Lorem ipsum

-   Lorem ipsum 

-   Lorem ipsum 

------------------------------------------------------------------------

## Deliverables {#lab3-deliverables .unnumbered}

-   Lorem ipsum

-   Lorem ipsum

-   Lorem ipsum

------------------------------------------------------------------------

## Data {.unnumbered}

Lorem ipsum

------------------------------------------------------------------------

## Task 1: Lorem ipsum {.unnumbered}

Lorem ipsum

**Step 1:** Lorem ipsum.

**Step 2:** Lorem ipsum.

**Step 3:** Lorem ipsum.

__HINT: Lorem ipsum.__

##### Q1. LOREM IPSUM? {.unnumbered}

##### Q2. LOREM IPSUM? {.unnumbered}

------------------------------------------------------------------------

## Task 2: Lorem ipsum {.unnumbered}

Lorem ipsum

**Step 1:** Lorem ipsum.

**Step 2:** Lorem ipsum.

**Step 3:** Lorem ipsum.

__HINT: Lorem ipsum.__

##### Q3. LOREM IPSUM? {.unnumbered}

##### Q4. LOREM IPSUM? {.unnumbered}

------------------------------------------------------------------------

## Summary {.unnumbered}

Here

Return to the **[Deliverables](#lab3-deliverables)** section to check off everything you need to submit for credit in the course management system.
